\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\setmainfont{Bodoni 72 Book}
\usepackage[paperwidth=11in,paperheight=17in,margin=1in,headheight=0.0in,footskip=0.5in,includehead,includefoot,portrait]{geometry}
\usepackage[absolute]{textpos}
\TPGrid[0.5in, 0.25in]{23}{24}
\parindent=0pt
\parskip=12pt
\usepackage{nopageno}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{amsmath}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}

\begin{document}

\begingroup
\begin{center}
\huge \textit{Devenir}
\end{center}
\endgroup

\begingroup
\begin{center}
or, \textit{flocks}
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
if our sacrum split and our ribs stood up,
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
like these black belts which hang vertically from the ground as we run
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and if we could pant out until our lungs sealed and our tongue could hang such to taste the blood on our chest
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and feel the pulse. perfectly. metronomic. slow. hard.
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
then we would know how our body feels
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
as we, near instantaneous, guide ourself between the trees,
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
``Did you hear that?"
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Here. Knots.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
He, looking out from where he sat,
\end{center}
\endgroup

\begingroup
\begin{center}
Noted how much warmer it looked than it was
\end{center}
\endgroup

\begingroup
\begin{center}
And brought it to the attention of the others in the house.
\end{center}
\endgroup

\begingroup
\begin{center}
They looked up,
\end{center}
\endgroup

\begingroup
\begin{center}
Nodded,
\end{center}
\endgroup

\begingroup
\begin{center}
Didn't seem to notice especially.
\end{center}
\endgroup

\begingroup
\begin{center}
Perhaps this was his sign to keep things to himself,
\end{center}
\endgroup

\begingroup
\begin{center}
Or to run again between the trees,
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
it's hot when we begin to run in circles
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and when we stop and lower ourselves as though worshipping
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
when we curve ourself behind and beneath
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
when we know what is us
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
by what she is
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and our heart is absorbed back into our chest, our bone reseals itself, and a flock of focus flies around either one of our eyes and rejoins itself, landing on our nose, instantly retracting all that we were in one beat
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
we become the one who kills
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Not. Is. When.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
Looking up from beneath the grass, you may see a songbird. It doesn't matter which kind. All you need is to see. You may be able to watch the way her neck moves. A glint of sun may fall off her feathers and into your eye. And if you don't rub the glint out, and if the grass doesn't obstruct your vision beyond what is beautiful, you may even know where she's looking just by watching her eyes. You might wonder how you know, if they're completely black eyes, and if they have no whiteness around the iris which you can track the direction of. How is it that you are so sure, more sure than you were sure that you loved her, that you know \textit{exactly} where she's looking?
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Knots. When. Here.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
``It's like there's someone talking . . . or playing something?"
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
You may be able to watch the way her neck moves. If you look up, if you can see, you may see where she's looking.
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
He, returned,
\end{center}
\endgroup

\begingroup
\begin{center}
With the base of his skull and the back of his knees wrapped around either arm of the chair,
\end{center}
\endgroup

\begingroup
\begin{center}
Noted the movement of the leaves,
\end{center}
\endgroup

\begingroup
\begin{center}
And saw them as a tree,
\end{center}
\endgroup

\begingroup
\begin{center}
And envied them.
\end{center}
\endgroup

\begingroup
\begin{center}
He remembered the sign,
\end{center}
\endgroup

\begingroup
\begin{center}
Kept his jealousy to himself,
\end{center}
\endgroup

\begingroup
\begin{center}
And listened to the playing, or the singing.
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
``You have to hear it."
\end{center}
\endgroup

\begingroup
\begin{center}
``Yeah, it's pretty quiet, but you hear it, right?"
\end{center}
\endgroup

\begingroup
\begin{center}
``I don't think it's that far away."
\end{center}
\endgroup

\begingroup
\begin{center}
``Have you ever been in the middle of a cave and been able to hear a conversation at the mouth as if they're right next to you, because of the echo?"
\end{center}
\endgroup

\begingroup
\begin{center}
``It's the opposite of that, I hate it."
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
If the grass isn't so much to obstruct your view, with the sun shining on the other side of it and turning it black against the sky, you may see her head jut towards the ground. In an instant, she may rise. Her and the grass may share a silhouette in front of the white sky, and you may be able to make out a beetle in her beak. Its abdomen might be bent between her jaws, and its wings may be disfigured, and its legs may rotate in six directions, and you may not be able to understand how you feel. You probably won't understand. You won't know what she has become to you, and this will scare you. If the wings splay outward when she crushes its outer shell and swallows as quickly as she rose, you will be afraid.
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
we know how our body feels in frozenness
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
we know how she will feel when our circle closes
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
as strange runes form in the lines we draw between ourself
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
around the one you knew you loved
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
she, at our center,
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
watching the movement of the leaves,
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
knows we're not with her
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
He was not with her
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Here.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
He was
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Here. Knots.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{6\baselineskip}

\begingroup
\begin{center}
He was not with her when he watched a songbird under the tree.
\end{center}
\endgroup

\begingroup
\begin{center}
It didn't matter which kind.
\end{center}
\endgroup

\begingroup
\begin{center}
All he needed was to see it alone at first,
\end{center}
\endgroup

\begingroup
\begin{center}
Then, like sand in a dune rolling down itself,
\end{center}
\endgroup

\begingroup
\begin{center}
He needed to see her siblings draw strange runes around her,
\end{center}
\endgroup

\begingroup
\begin{center}
And watch her disappear,
\end{center}
\endgroup

\begingroup
\begin{center}
Become nothing,
\end{center}
\endgroup

\begingroup
\begin{center}
No, something.
\end{center}
\endgroup

\begingroup
\begin{center}
A single cell of jutting and rising heads,
\end{center}
\endgroup

\begingroup
\begin{center}
Of splayed wings.
\end{center}
\endgroup

\begingroup
\begin{center}
He swiveled to call,
\end{center}
\endgroup

\begingroup
\begin{center}
Found no one,
\end{center}
\endgroup

\begingroup
\begin{center}
Kept to himself.
\end{center}
\endgroup

\begingroup
\begin{center}
He was not
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Is. Here. Knots.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
If she becomes a cell, you won't see a silhouette. The gaps of white in the sky become black will be easier identified. You will 
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Here.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
You will hear the crunch of beetles. You may deny that is what you're hearing. You will hear the crunch of beetles. You will look up. You will
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Knots. Here.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
``You're fucking lying, you hear that."
\end{center}
\endgroup

\begingroup
\begin{center}
``You have to hear it."
\end{center}
\endgroup

\begingroup
\begin{center}
``The fucking singing!"
\end{center}
\endgroup

\begingroup
\begin{center}
``You have to hear there are fucking words!"
\end{center}
\endgroup

\begingroup
\begin{center}
``There are words they're lies,"
\end{center}
\endgroup

\begingroup
\begin{center}
``You're fucking lying, they're lies!"
\end{center}
\endgroup

\begingroup
\begin{center}
``They're fucking lies!"
\end{center}
\endgroup

\begingroup
\begin{center}
``I'm not with her!"
\end{center}
\endgroup

\begingroup
\begin{center}
``He's not with her, she's not"
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
she's here with us when we close
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
when we become a cell, and she our nucleus,
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and she is no longer the one who looks to the trees
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
she is the one who screams
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
the one who retreats,
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
the one who fails
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
the one whose skin is gently pressed against a thousand jaws
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
and for whom we freeze
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
for whom she is frozen
\rightskip\leftskip
\end{center}
\endgroup

\begingroup
\begin{center}
\leftskip0.5in
when the
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
When her head juts over you, you will look up into her throat, and touch the inside of her beak, the top with your left hand, the bottom with your right, and you will freeze. So will she. You'll hear the beetles. You may feel gentle. Your pulse may slow. Your surroundings may still. For a moment, the crackle of shell and leg may be the most beautiful song you've ever heard. And then, your hands will be pressed closer to your body. Her skin will press closer to our jaw.
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
He, and no one else, watched you and she,
\end{center}
\endgroup

\begingroup
\begin{center}
As space closed.
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
and what do I become when she, in knots, guides ourself between the trees? and what do I become when we, near instantaneous, have to hear? and what do I become when there are fucking words, here, is knots? and what do I become when he juts and rises, his sacrum split in belts? and what do I become when we watch the movements of the leaves, brought it to the attention of the others in the house, keep it to herself? and what do I become when I was sure I loved her? and what do I become when ``I don't believe it?" ``I don't believe her?" ``I don't believe her?" ``I don't believe it?" ``I don't believe it?" ``I don't believe her?" ``I don't believe it?" ``I don't believe her?" ``I don't believe her?" ``I don't believe her?"
\end{center}
\endgroup

\vspace*{2\baselineskip}

\begingroup
\begin{center}
\leftskip0.5in
Here. Is. Not.
\rightskip\leftskip
\end{center}
\endgroup

\vspace*{4\baselineskip}

\begingroup
\begin{center}
``My best friend told me about the prophetess Cassandra."
\end{center}
\endgroup

\begingroup
\begin{center}
``How she never lied, and was never believed."
\end{center}
\endgroup

\begingroup
\begin{center}
``When I met her, and her hair reminded me of my best friend's cello,"
\end{center}
\endgroup

\begingroup
\begin{center}
``I told her about her name, what it meant."
\end{center}
\endgroup

\begingroup
\begin{center}
``She smiled."
\end{center}
\endgroup

\begingroup
\begin{center}
``And I could tell where she was looking just by watching her eyes."
\end{center}
\endgroup

\begingroup
\begin{center}
``And I was sure I loved her."
\end{center}
\endgroup

\begingroup
\begin{center}
``Or maybe I met my best friend after"
\end{center}
\endgroup

\begingroup
\begin{center}
``And I never told the prophetess her name,"
\end{center}
\endgroup

\begingroup
\begin{center}
``Because I didn't know it,"
\end{center}
\endgroup

\begingroup
\begin{center}
``I couldn't have."
\end{center}
\endgroup

\begingroup
\begin{center}
``I don't remember."
\end{center}
\endgroup

\begingroup
\begin{center}
``My god, I really don't remember."
\end{center}
\endgroup

\end{document}